Estimating duration in the presence of misclassification

### 2024-03-25 ATACCC-appendix-original-analysis.tex
proof

For an individual $i$, their trajectory is determined by two points and one slope parameter.
The points are the time at which the individual has a 50\% chance of testing positive, $t_{i,0}$, and the time at which their viral load
peaks, $t_{i,\text{peak}}$ after $t_{i,0}$; the slope parameter, $\beta_i$ determines the rate their Ct increases (viral load decreases) following the peak.
The Ct value for an individual at time $t_{i,0}$ is the known limit of detection, $C_\text{lod}$,
Their Ct value at the peak is $C_{i,\text{peak}}$ and inferred.
The slope parameter, $\beta_i$, determines how quickly an individual's Ct value increases following the peak viral load.
We denote the vector of the parameters defined here as $\vec\theta_i = \begin{bmatrix} t_{i,0} & t_{i,\text{peak}} & C_{i,\text{peak}} &  \beta_i \end{bmatrix}^T$.

>>>>

For an individual $i$, their trajectory is determined by two points and one slope parameter.
The points are the time at which the individual has a 50\% chance of testing positive, $t_{i,0}$, and the time at which their viral load.
peaks, $t_{i,\text{peak}}$ after $t_{i,0}$; the slope parameter, $\beta_i$ determines the rate their Ct increases (viral load decreases) following the peak.
The Ct value for an individual at time $t_{i,0}$ is the known limit of detection, $C_\text{lod}$,
Their Ct value at the peak is $C_{i,\text{peak}}$ and inferred.
The slope parameter, $\beta_i$, determines how quickly an individual's Ct value increases following the peak viral load.
We denote the vector of the parameters defined here as $\vec\theta_i = \begin{bmatrix} t_{i,0} & t_{i,\text{peak}} & C_{i,\text{peak}} &  \beta_i \end{bmatrix}^T$.

### 2024-03-25 biology-data.tex
proof

SARS-CoV-2 is closely related to previous coronaviruses that have caused outbreaks in humans, SARS-CoV and MERS-CoV.
Coronaviruses are RNA (Ribonucleic acid) viruses.
RNA viruses use RNA, rather than DNA, as their genetic material.
RNA viruses, which include influenza, mutate rapidly and are the most likely class of viruses to cause pandemics~\autocite{woolhouseRNA}.

The initial and most sensitive diagnostic test for SARS-CoV-2 uses RT-PCR, which I explain in \cref{biology-data:sec:PCR}.
SARS-CoV-2 causes the disease COVID-19; I discuss the \emph{natural history} of the disease, the course it takes from beginning to end~\autocite[193]{portaEpiDictionary}, in \cref{biology-data:sec:natural-history}.

@@

PCR (Polymerase Chain Reaction) is a procedure that produces millions to billions of copies of a specific segment of DNA (Deoxyribonucleic acid) from a single copy~\autocite{smithPCR,garibyanPCR}.
This is known as \emph{amplifying} the DNA.
PCR has many uses within the biological sciences; Mark R.\ Hughes, deputy director of the Human Genome Project, has claimed it is the most important scientific technology of the last hundred years~\autocite{powledgePCR}.
It is central to the work in this thesis because it can detect the presence of SARS-CoV-2 in a sample taken from a human, most commonly a nose and/or throat swab.

@@

The process is a series of cycles, each cycle containing three steps~\autocite{powledgePCR,garibyanPCR}.
The first step, \emph{denaturation}, heats the DNA causing its two strands to separate.
The second step, \emph{annealing}, lowers the temperature, causing the primers to bind to the DNA.
The final step, \emph{extension}, raises the temperature, causing the DNA polymerase to replicate the DNA sequence between the primers. 
In the course of such a cycle, the amount of DNA doubles.
Therefore, the number of DNA copies increases geometrically with the number of cycles completed.

@@

% The Ct value decreases as the amount of DNA present in the original sample increases~\autocite{hanRTPCR}.
If there is more RNA present, reverse transcription creates proportionally more DNA.
More initial DNA means fewer cycles until detection; that is, the Ct value is lower~\autocite{hanRTPCR}.
The number of DNA copies doubles each cycle, therefore the log Ct value decreases linearly with the quantity of RNA or DNA in the original sample (see \cref{biology-data:fig:ct-calibration}).
A \emph{standard curve} translates the Ct value to viral load for a given test.
A standard curve is produced by measuring the Ct value using reference samples with known viral load, and, as seen in \cref{biology-data:fig:ct-calibration}, they vary between studies.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{biology-data/ct-calibration}
    \caption[Example standard Ct curves]{%
        Example standard curves, which relate the logarithm of the viral copy number (the number of copies of the target DNA or RNA in the sample) to the measured Ct value.
        Reproduced from \textcite{hanRTPCR} with permission.
    }
    \label{biology-data:fig:ct-calibration}
\end{figure}

@@

An important concept throughout this thesis will be that of \emph{detectable} individuals.
An individual is defined as detectable between the time they would first test positive on a perfect RT-PCR test (if tested) and the time they would stop doing so.
It is not possible to conclusively determine whether an individual is detectable because perfect RT-PCR tests do not exist (see \cref{biology-data:sec:PCR}).
However, viewing the number of RNA genome copies in an individual as a latent process this can then be defined as the time when the number of RNA genome copies is above the limit of detection of the RT-PCR test (defined in \cref{biology-data:sec:measurement-error}).
% While this definition is not perfectly precise, it is clear enough for the purposes it used in this thesis.

@@

The time for each of these stages depends on various features of host and virus characteristics and has a large amount of variation.
In this thesis, I focus on pre-Alpha variants of SARS-CoV-2 in unvaccinated individuals.
The time from infection to infectiousness is known as the \emph{latent period}.
The length of the latent period is hard to estimate because we rarely observe either the time of infection or the start of infectiousness.
Estimates of its length are based on careful contact tracing, where transmission times are thought to be known with a reasonable degree of certainty.
These estimates vary but suggest a mean length of 3--4 days for pre-Alpha variants~\autocite[and references therein]{zhaoEstimating}.
The time from infection to experiencing symptoms is known as the \emph{incubation period}; it is undefined for asymptomatic individuals.
As the symptom onset time (when symptoms start) is often known, this is easier to estimate than the latent period.
However, the unknown infection time still poses challenges, again requiring contact tracing data.
Therefore, estimates are sensitive to the choice of data and statistical model.
Its mean length is around 6 days~\autocite{wuIncubation,quesadaIncubation,aleneSerial}.

A host's \emph{viral load}, the quantity of viral particles in a host, is the underlying biological process driving the different periods and characteristics of an infection~\autocite{puhachSARSCoV2}.
Any host's viral load is determined by the interaction of many biological processes, most prominently the virus's replication increasing the viral load and the host's immune response reducing the viral load~\autocite{keVivo}.
Viral replication requires the virus to infect a host cell and then use the host cell's machinery to produce more virus; as more host cells are infected this process slows because there are fewer remaining potential host cells, known as \emph{target cells}, to infect.
Host cells which can potentially be infected are known as \emph{target cells}.
The rate at which host cells are infected slows over time because there are fewer remaining target cells to infect.
The host's immune system can slow this process by various mechanisms; the most relevant for SARS-CoV-2 is by making some target cells less susceptible to infection.
A host's immune response is triggered by the viral load and becomes stronger as the viral load increases.
A high viral load is associated with being more infectious, more likely to test positive on an RT-PCR test, and the start of symptoms~\autocite{puhachSARSCoV2,keVivo}.

@@

Of the 738 contacts enrolled, 172 (23\%) had at least one positive test
\Textcite{hakkiOnset} analysed the 57 contacts who tested positive for SARS-CoV-2 and had the growth phase in their viral load measured.
They excluded the remaining 115 contacts with at least one positive RT-PCR test, ATACCC did not capture the phase of the infection with increasing viral load.
This exclusion was to ensure viral load trajectories are identifiable.
I will revisit and extend this analysis in \cref{E-ATACCC}.

>>>>

SARS-CoV-2 is closely related to previous coronaviruses that have caused outbreaks in humans, including SARS-CoV and MERS-CoV.
Coronaviruses are RNA (Ribonucleic acid) viruses.
RNA viruses use RNA, rather than DNA (Deoxyribonucleic acid), as their genetic material.
RNA viruses, which include influenza, mutate rapidly and are the most likely class of viruses to cause pandemics~\autocite{woolhouseRNA}.

The initial and most sensitive diagnostic test for SARS-CoV-2 uses RT-PCR, which I explain in \cref{biology-data:sec:PCR}.
I discuss the SARS-CoV-2 infection \emph{natural history}, the course it takes from beginning to end~\autocite[193]{portaEpiDictionary}, in \cref{biology-data:sec:natural-history}.

@@

PCR (Polymerase Chain Reaction) is a procedure that produces millions to billions of copies of a specific segment of DNA  from a single copy~\autocite{smithPCR,garibyanPCR}.
This is known as \emph{amplifying} the DNA.
PCR has many uses within the biological sciences; Mark R.\ Hughes, deputy director of the Human Genome Project, has claimed it is the most important scientific technology of the last hundred years~\autocite{powledgePCR}.
It is central to the work in this thesis because it can detect the presence of SARS-CoV-2 in a sample taken from a human, most commonly a nose and/or throat swab.

@@

The PCR process is a series of cycles, each cycle containing three steps~\autocite{powledgePCR,garibyanPCR}.
The first step, \emph{denaturation}, heats the DNA causing its two strands to separate.
The second step, \emph{annealing}, lowers the temperature, causing the primers to bind to one of the strands of DNA.
The final step, \emph{extension}, raises the temperature, causing the DNA polymerase to replicate the DNA sequence between the primers. 
In the course of such a cycle, the amount of DNA doubles.
Therefore, the number of DNA copies increases geometrically with the number of cycles completed.

@@

% The Ct value decreases as the amount of DNA present in the original sample increases~\autocite{hanRTPCR}.
If there is more RNA present, reverse transcription creates proportionally more DNA.
More initial DNA means fewer cycles until detection; that is, the Ct value is lower~\autocite{hanRTPCR}.
The number of DNA copies doubles each cycle, therefore the log Ct value decreases linearly with the quantity of RNA or DNA in the original sample (see \cref{biology-data:fig:ct-calibration}).
A \emph{standard curve}, also known as a \emph{calibration curve}, translates the Ct value to viral load for a given test~\autocite{bustinMIQE}.
A standard curve is produced by measuring the Ct value using reference samples with known viral load, and, as seen in \cref{biology-data:fig:ct-calibration}, they vary between studies.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{biology-data/ct-calibration}
    \caption[Example standard Ct curves]{%
        Example standard curves, which relate the logarithm of the viral copy number (the number of copies of the target DNA or RNA in the sample) to the measured Ct value.
        Reproduced from \textcite{hanRTPCR} with permission.
    }
    \label{biology-data:fig:ct-calibration}
\end{figure}

@@

An important concept throughout this thesis will be that of \emph{detectable} individuals.
An individual is defined as detectable between the time they would first test positive on a perfect RT-PCR test (if tested) and the time they would stop doing so.
It is not possible to conclusively determine whether an individual is detectable because perfect RT-PCR tests do not exist.
However, viewing the number of RNA genome copies in an individual as a latent process, this can then be defined as the time when the number of RNA genome copies is above the limit of detection of the RT-PCR test (defined in \cref{biology-data:sec:measurement-error}).
% While this definition is not perfectly precise, it is clear enough for the purposes it used in this thesis.

@@

The time for each of these stages depends on various features of host and virus characteristics and has a large amount of variation.
In this thesis, I focus on pre-Alpha variants of SARS-CoV-2 in unvaccinated individuals.
The time from infection to infectiousness is known as the \emph{latent period}~\autocite{goughEstimation}.
The length of the latent period is hard to estimate because we rarely observe either the time of infection or the start of infectiousness.
Estimates of its length are based on careful contact tracing, where transmission times are thought to be known with a reasonable degree of certainty.
These estimates vary but suggest a mean length of 3--4 days for pre-Alpha variants~\autocite[and references therein]{zhaoEstimating}.
The time from infection to experiencing symptoms is known as the \emph{incubation period}; it is undefined for asymptomatic individuals~\autocite{portaEpiDictionary}.
As the symptom onset time (when symptoms start) is often known, this is easier to estimate than the latent period.
However, the unknown infection time still poses challenges, again requiring contact tracing data.
Therefore, estimates are sensitive to the choice of data and statistical model.
Its mean length is around 6 days~\autocite{wuIncubation,quesadaIncubation,aleneSerial}.

A host's \emph{viral load}, the quantity of viral particles in a host, is the underlying biological process driving the different periods and characteristics of an infection~\autocite{puhachSARSCoV2}.
Any host's viral load is determined by the interaction of many biological processes, most prominently the virus's replication increasing the viral load and the host's immune response reducing the viral load~\autocite{keVivo}.
Viral replication requires the virus to infect a host cell and then use the host cell's machinery to produce more virus; as more host cells are infected this process slows because there are fewer remaining potential host cells, known as \emph{target cells}, to infect.
The rate at which host cells are infected slows over time because there are fewer remaining target cells to infect.
The host's immune system can slow this process by various mechanisms; the most relevant for SARS-CoV-2 is by making some target cells less susceptible to infection.
A host's immune response is triggered by the viral load and becomes stronger as the viral load increases.
A high viral load is associated with being more infectious, more likely to test positive on an RT-PCR test, and the start of symptoms~\autocite{puhachSARSCoV2,keVivo}.

@@

Of the 738 contacts enrolled, 172 (23\%) had at least one positive test.
\Textcite{hakkiOnset} analysed the 57 contacts who tested positive for SARS-CoV-2 and had the growth phase in their viral load measured.
They excluded the remaining 115 contacts with at least one positive RT-PCR test, ATACCC did not capture the phase of the infection with increasing viral load.
This exclusion was to ensure viral load trajectories are identifiable.
I will revisit and extend this analysis in \cref{E-ATACCC}.

### 2024-03-25 cis-imperfect-testing.tex
proof ch 5
plural data
proof

% Discussion and interrogation of the data led me to
I hypothesised that the reason for the unexpectedly high number of single positive episodes (compared to simulation) was the presence of false negative results.
There are several strands of evidence supporting this hypothesis.
First, it is well known that RT-PCR testing can return false negatives  (see \cref{E-biology-data:sec:PCR}); I explicitly include them in the viral load model of \cref{E-ATACCC}.
Intermittent negatives (described in  \cref{E-biology-data:sec:PCR}) show that they occur within the CIS.
Furthermore, in \cref{imperf-test:sec:simulate}, I expanded the simulation study of \cref{E-perf-test:sec:simulation-study} to include false negatives (see  for more details).
This reproduced the CIS data more faithfully and exhibited the same issues when estimating the duration distribution (see \cref{imperf-test:fig:sim-single-pos}).
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/sim-single-positive-episodes}
  \caption[Single positive episodes in CIS simulation]{%
    Proportion of detected episodes which have a single positive episode.
    y-axis is the number of simulations, out of \numprint{1000}, with the indicated proportion.
    Test sensitivity is $\psens$.
    The CIS data is shown as a vertical line.
  }
  \label{imperf-test:fig:sim-single-pos}
\end{figure}

@@

The CIS data provides evidence for a test sensitivity declining over the course of an episode.
\Cref{imperf-test:fig:bounding-cis-sensitivity} demonstrates this by using the following classification for test results.
\begin{enumerate}
    \item All positive results are true positives.
    \item All intermittent negatives are false negatives.
    \item The negative at the end of an episode is a possible false negative.
    \item All other negatives are true negatives.
\end{enumerate}
Here, I am assuming that the probability of two false negative tests at the end of an episode is negligible.
As test sensitivity is the proportion of individuals who should test positive that do so, it can be empirically calculated as number of true positives / (number of true positives + number of false negatives).
Therefore, I calculate the test sensitivity for each day, considering the first positive result in an episode as day 0.
As the latent start day of the infection episode is before the first positive result, day 0 reflects some unknown number of days into the infection episode.
I bound the test sensitivity on each day by assuming either all or none of the possible false negatives (group 3) are in fact false negatives.
% In \cref{imperf-test:fig:bounding-cis-sensitivity} we consider the values produced by assuming the negative following the last positive in an episode could be either a true or false negative as a function of time since the individual was detected (\ie: the first positive test in the episode).
This generates broad bounds, although suggest a declining test sensitivity over the course of an episode (see \cref{imperf-test:fig:bounding-cis-sensitivity}).
Small numbers of tests mean that the series is noisy near the start and the end, such as both bounds being 0 on some days after day 40.
However, the general trend is clear.
\begin{figure}
  \includegraphics{cis-imperfect-testing/test-sens-bound}
  \caption[Bounding test sensitivity using CIS data]{
    Bounding the test sensitivity using CIS data as a function of time since the infection was detected.
  }
  \label{imperf-test:fig:bounding-cis-sensitivity}
\end{figure}

@@

When $\psens = 0.8$ and is correctly specified, the model recovers the true survival time well (see \cref{imperf-test:fig:constant-test-sensitivity}(B)).
The informative prior, in comparison to the vague prior, helps to overcome the misspecification due to the simplifying assumptions, moving the estimated survival function closer to its true survival time.
However, when $\psens = 0.6$, this is no longer the case (see \cref{imperf-test:fig:constant-test-sensitivity}(A)).
This is likely caused by too large a violation of the simplifying assumptions made in \cref{imperf-test:sec:modelling}.
\begin{figure}
  % \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}}
  \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}
  \caption[Simulation study results with constant test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a correctly specified test sensitivity.
    The true survival time is shown in black
  }
  \label{imperf-test:fig:constant-test-sensitivity}
\end{figure}

Next, I considered the consequence of $\psens$ being misspecified, I use the model combination prior because it is the better performing prior in the correctly specified case.
If the test sensitivity is misspecified, that is the assumed value for $p_\text{sens}$ in \cref{imperf-test:eq:pit-prime,imperf-test:eq:pit-prime} is different to the value used in the simulation, then the survival time will be biased (see \cref{imperf-test:fig:misspecified-test-sensitivity}).
If $\psens$ is misspecified and too low (see \cref{imperf-test:fig:misspecified-test-sensitivity}(A)), then the posterior estimate initially follows the true value but then separates.
The number of episodes inferred to have truly ended by the first negative is too high, and hence the survival time is overestimated.
This effect dominates over the opposing bias of overestimating the number of undetected episodes.
The opposite occurs if the test sensitivity is assumed to be too high, although the posterior moves away from the truth earlier (see \cref{imperf-test:fig:misspecified-test-sensitivity}(C)).
\begin{figure}
  % \makebox[\textwidth][c]{
    \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-misspecified-sensitivity}
  \caption[Simulation study results with misspecified test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a possibly misspecified test sensitivity.
    The true survival time is shown in black
    All simulations use a constant test sensitivity of 0.8, but the inference procedure assumes different values, as per the key.
    Hence, (B) is correctly specified but (A) and (C) have misspecified $\psens$.
  }
  \label{imperf-test:fig:misspecified-test-sensitivity}
\end{figure}

@@

% However, comparing the CIS and simulated datasets do not show any differences which suggest what in the data is causing these differences.
% Then, the additional undetected infections implied by a 
% This would lead to more undetected infections than the model assumes, and hence a higher $\ntot$ is required to explain the data.

>>>>

% Discussion and interrogation of the data led me to
I hypothesised that the reason for the unexpectedly high number of single positive episodes (compared to simulation) was the presence of false negative results.
There are several strands of evidence supporting this hypothesis.
First, it is well known that RT-PCR testing can return false negatives  (see \cref{E-biology-data:sec:PCR}); I explicitly include them in the viral load model of \cref{E-ATACCC}.
Intermittent negatives (described in  \cref{E-biology-data:sec:PCR}) show that they occur within the CIS.
Furthermore, in \cref{imperf-test:sec:simulate}, I expanded the simulation study of \cref{E-perf-test:sec:simulation-study} to include false negatives (see  for more details).
This reproduced the CIS data more faithfully and exhibited the same issues when estimating the duration distribution (see \cref{imperf-test:fig:sim-single-pos}).
\begin{figure}
  \centering \includegraphics{cis-imperfect-testing/sim-single-positive-episodes}
  \caption[Single positive episodes in CIS simulation]{%
    Proportion of detected episodes which have a single positive episode.
    y-axis is the number of simulations, out of \numprint{1000}, with the indicated proportion.
    Test sensitivity is $\psens$.
    The CIS data are shown as a vertical line.
  }
  \label{imperf-test:fig:sim-single-pos}
\end{figure}

@@

The CIS data provides evidence for a test sensitivity declining over the course of an episode.
\Cref{imperf-test:fig:bounding-cis-sensitivity} demonstrates this by using the following classification for test results.
\begin{enumerate}
    \item All positive results are true positives.
    \item All intermittent negatives are false negatives.
    \item The negative at the end of an episode is a possible false negative.
    \item All other negatives are true negatives.
\end{enumerate}
Here, I am assuming that the probability of two false negative tests at the end of an episode is negligible.
As test sensitivity is the proportion of individuals who should test positive that do so, it can be empirically calculated as number of true positives / (number of true positives + number of false negatives).
Therefore, I calculate the test sensitivity for each day, considering the first positive result in an episode as day 0.
As the latent start day of the infection episode is before the first positive result, day 0 reflects some unknown number of days into the infection episode.
I bound the test sensitivity on each day by assuming either all or none of the possible false negatives (group 3) are in fact false negatives.
% In \cref{imperf-test:fig:bounding-cis-sensitivity} we consider the values produced by assuming the negative following the last positive in an episode could be either a true or false negative as a function of time since the individual was detected (\ie the first positive test in the episode).
This generates broad bounds, although suggest a declining test sensitivity over the course of an episode (see \cref{imperf-test:fig:bounding-cis-sensitivity}).
Small numbers of tests mean that the series is noisy near the start and the end, such as both bounds being 0 on some days after day 40.
However, the general trend is clear.
\begin{figure}
  \includegraphics{cis-imperfect-testing/test-sens-bound}
  \caption[Bounding test sensitivity using CIS data]{
    Bounding the test sensitivity using CIS data as a function of time since the infection was detected.
  }
  \label{imperf-test:fig:bounding-cis-sensitivity}
\end{figure}

@@

When $\psens = 0.8$ and is correctly specified, the model recovers the true survival time well (see \cref{imperf-test:fig:constant-test-sensitivity}(B)).
The informative prior, in comparison to the vague prior, helps to overcome the misspecification due to the simplifying assumptions, moving the estimated survival function closer to its true survival time.
However, when $\psens = 0.6$, this is no longer the case (see \cref{imperf-test:fig:constant-test-sensitivity}(A)).
This is likely caused by too large a violation of the simplifying assumptions made in \cref{imperf-test:sec:modelling}.
\begin{figure}
  % \makebox[\textwidth][c]{\includegraphics[width=1.2\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}}
  \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-constant-sensitivity}
  \caption[Simulation study results with constant test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a correctly specified test sensitivity.
    The true survival time is shown in black.
  }
  \label{imperf-test:fig:constant-test-sensitivity}
\end{figure}

Next, I considered the consequence of $\psens$ being misspecified, I use the model combination prior because it is the better performing prior in the correctly specified case.
If the test sensitivity is misspecified, that is the assumed value for $p_\text{sens}$ in \cref{imperf-test:eq:pit-prime,imperf-test:eq:pit-prime} is different to the value used in the simulation, then the survival time will be biased (see \cref{imperf-test:fig:misspecified-test-sensitivity}).
If $\psens$ is misspecified and too low (see \cref{imperf-test:fig:misspecified-test-sensitivity}(A)), then the posterior estimate initially follows the true value but then separates.
The number of episodes inferred to have truly ended by the first negative is too high, and hence the survival time is overestimated.
This effect dominates over the opposing bias of overestimating the number of undetected episodes.
The opposite occurs if the test sensitivity is assumed to be too high, although the posterior moves away from the truth earlier (see \cref{imperf-test:fig:misspecified-test-sensitivity}(C)).
\begin{figure}
  % \makebox[\textwidth][c]{
    \includegraphics[width=\textwidth]{cis-imperfect-testing/sim-misspecified-sensitivity}
  \caption[Simulation study results with misspecified test sensitivity]{%
    Posterior (median and 95\% credible interval) of the survival time for the simulation study with a possibly misspecified test sensitivity.
    The true survival time is shown in black.
    All simulations use a constant test sensitivity of 0.8, but the inference procedure assumes different values, as per the key.
    Hence, (B) is correctly specified but (A) and (C) have misspecified $\psens$.
  }
  \label{imperf-test:fig:misspecified-test-sensitivity}
\end{figure}

@@

% However, comparing the CIS and simulated datasets do not show any differences which suggest what in the data are causing these differences.
% Then, the additional undetected infections implied by a 
% This would lead to more undetected infections than the model assumes, and hence a higher $\ntot$ is required to explain the data.
